\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Minor fixes to directed and new graph

\paragraph{Estimating $V$}
Finally, we can estimate $V$ by renormalizing the third-order moments $\mO_{234} \eqdef \Pr(x^a_2, x^a_3, x^a_4)$,
which can be obtained analogously:
\begin{align*}
  \mO_{234} = \mH_{234}(O, O, O) \quad\Rightarrow\quad
  \mH_{234} = \mO_{234}(\pinv O, \pinv O, \pinv O).
\end{align*}

>>>>

\paragraph{Estimating $V$}
Finally, we can estimate $V$ by renormalizing the hidden marginals
$\mH_{234} \eqdef \Pr(h_2, h_3, h_4)$ from the third-order moments
$\mO_{234} \eqdef \Pr(x^a_2, x^a_3, x^a_4)$:
\begin{align*}
  \mO_{234} = \mH_{234}(O, O, O) \quad\Rightarrow\quad
  \mH_{234} = \mO_{234}(\pinv O, \pinv O, \pinv O).
\end{align*}
